SciPy - some descriptive title here

### 2018-04-16 scipy-1.0/paper.tex
MAINT: add position flag for figure
ENH: update asv benchmarks with additional version of Cython.

    \begin{figure}
        \centering
        \includegraphics[width=\textwidth]{static/asv_time_query_ckdtree}
        \caption{Airspeed velocity benchmarks for scipy.spatial.cKDTree.query() over a roughly nine year commit history time frame. The results are based on Python 2.7 performance on the master branch of the project using numpy 1.8.2 and Cython versions 0.27.3 and 0.21.1 (for improved backward compatibility). Only the L2 (Euclidean) norm is shown here, and to improve backward compatibility and sampling of the benchmarks there was no application of toroidal topology to the KDTree (boxsize argument was ignored).}
        \label{fig:asvbench}
    \end{figure}

>>>>

    \begin{figure}[H]
        \centering
        \includegraphics[width=\textwidth]{static/asv_time_query_ckdtree}
        \caption{Airspeed velocity benchmarks for scipy.spatial.cKDTree.query() over a roughly nine year commit history time frame. The results are based on Python 2.7 performance on the master branch of the project using numpy 1.8.2 and Cython versions 0.27.3, 0.21.1, and 0.18 (for improved backward compatibility). Only the L2 (Euclidean) norm is shown here, and to improve backward compatibility and sampling of the benchmarks there was no application of toroidal topology to the KDTree (boxsize argument was ignored).}
        \label{fig:asvbench}
    \end{figure}
